\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[pdftex,hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeEduLine}[3]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} \textit{\small ---\ #2} & \textit{#3} \\
\end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeItem}[1]{
\item\small{#1}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,itemsep=2pt,topsep=2pt,parsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt,topsep=1pt,parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-----------------------------
%%%%%%CV STARTS HERE%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{center}
{\LARGE \textbf{Aadi Amritraj Gupta}} \\ \vspace{2pt}
\small +91 9910265003 \ $|$ \ \href{mailto:getaadigupta2@gmail.com}{getaadigupta2@gmail.com} \ $|$ \ \href{https://www.linkedin.com/in/aadi-amritraj-gupta-328314260/}{linkedin.com/in/aadi-amritraj-gupta-328314260}
\end{center}
\vspace{-4pt}

%-----------SUMMARY-----------------
\section{Summary}
\small Python-focused developer building financial risk applications in technology consulting. Shipped an RBI-compliant credit-risk platform to production for a banking client, with hands-on experience across Python, SQL, Flask REST APIs, and Docker-based on-premises deployment. Keen to build modular, efficient applications at the intersection of technology, financial data, and portfolio analytics.

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Grant Thornton Bharat}{Feb 2025 -- Present}
{Senior Associate, Technology Consulting (started as Summer Trainee)}{}
\resumeItemListStart
\resumeItem{Shipped an RBI-compliant Expected Credit Loss (ECL) platform -- an in-house credit-risk product now being rolled out to further clients -- to production for a banking client, owning the backend and data layer end-to-end; deployed on-premises across Linux servers using Docker containers.}
\resumeItem{Built data-ingestion and validation pipelines delivering clean, consistent loan data for credit-risk computations, engineered for repeatable and consistent execution across runs.}
\resumeItem{Supported the platform's go-live by hardening backend stability, validating data accuracy, and enforcing regulatory compliance.}
\resumeItem{Architected RESTful APIs in Python and Flask connecting front-end interfaces to core business logic and database systems, exposing 200+ endpoints across 30+ services.}
\resumeItem{Developed backend systems in Python, SQL, and Flask for an internal Early Warning Signal (EWS) financial-risk-monitoring application, building the data-ingestion and signal-computation logic.}
\resumeItem{Conducted market research and price-discovery analysis of cybersecurity vendors for a banking client, evaluating 50+ vendors on capability and pricing to inform procurement strategy.}
\resumeItem{Partnered with consulting teams to translate business requirements into modular, scalable solutions deployable across multiple environments.}
\resumeItemListEnd

\resumeSubheading
{Boeing}{Jun 2024 -- Jul 2024}
{Systems Service Engineer Intern}{}
\resumeItemListStart
\resumeItem{Helped initiate an internal Flask-based web application that indexed all damage and issue categories into a searchable catalog, streamlining maintenance workflows .}
\resumeItem{Analyzed maintenance data and generated reports for resolving issues and supporting operational decisions.}
\resumeItemListEnd

\resumeSubheading
{General Electric Power}{Jul 2023}
{Industrial Trainee}{}
\resumeItemListStart
\resumeItem{Analyzed hydroelectric and pumped-storage operations from real-time telemetry, studying performance metrics and predictive-maintenance practices.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=1pt,parsep=0pt]
\resumeItem{\textbf{Languages \& Data:} Python, SQL, Pandas, NumPy, Data Analysis, Data Visualization, Advanced Excel, BI Tools}
\resumeItem{\textbf{Backend \& Infrastructure:} Flask, REST APIs, Docker, Linux, Git, Jupyter, MATLAB/Simulink}
\resumeItem{\textbf{Finance Domain:} Financial Risk Management, Expected Credit Loss (ECL), RBI Regulatory Compliance, Market Research, Business \& Stakeholder Analysis}
\end{itemize}

%-----------PROJECTS-----------------
\section{Projects}
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=1pt,parsep=0pt]
\resumeItem{\textbf{Real Estate Price Prediction Model:} Built regression models in Python and scikit-learn to predict property prices, applying feature engineering to improve accuracy.}
\resumeItem{\textbf{IR-Based Digital Tachometer:} Developed an Arduino system with Python logging for RPM analysis and signal-processing improvements.}
\resumeItem{\textbf{IoT Plant Watering System:} Designed a sensor-based automated irrigation system with real-time monitoring.}
\end{itemize}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeEduLine{Manipal Institute of Technology, Udupi}{B.Tech EEE, Minor in Data Science (CGPA: 7.19)}{2021 -- 2025}
\resumeEduLine{Amity International School, Saket, Delhi}{Class XII, 94.8\%}{2021}
\resumeEduLine{Amity International School, Gurugram}{Class X, 94\%}{2019}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS & LEADERSHIP-----------------
\section{Certifications \& Leadership}
\begin{itemize}[leftmargin=*,itemsep=0pt,topsep=1pt,parsep=0pt]
\resumeItem{\textbf{Certifications:} Python for Data Science, AI and Development (IBM); SQL for Data Science (UC Davis); Financial Markets (Yale University) -- all via Coursera}
\resumeItem{\textbf{Leadership:} Treasurer \& Technical Head, IE EnE (Manipal) -- organized workshops, site visits, and chapter finances; Management Committee, Research Society Manipal; Organizer, Techtatva technical fest}
\end{itemize}

\end{document}